\documentclass{article}

\usepackage{amssymb}

\title{Response to reviewers}
\author{A game theoretic model of the behavioural gaming that takes \\
place at the ED-EMS interface}

\begin{document}
    \maketitle

    The authors would like to thank once again all the reviewers for their
    constructive feedback and for
    the time they took to review the manuscript.
    We are also pleased to see that the reviewers feel that the revision has
    addressed their comments and that the manuscript presents scientifically
    correct and useful results.
    We have made the remaining requested minor changes and also provide a
    response to one of the reviewers whose remaining concern is about the fit
    of this paper for EJOR.
    Our main arguments are:
    \begin{itemize}
        \item Our paper provides theoretical results and insights
        \item There is a number of pages in EJOR that are similar to ours
        \item The EJOR scope does not emphasise that a paper should present a
        new theorem in order to be published
    \end{itemize}


    \line(1, 0){0.92\textwidth}
    \begin{itemize}
        \item Reviewer 1: \textit{The following two papers are related to the
        current work and I suggest the authors add them in the references with
        citations in the literature review: \\
        1. Chen, W., Z. G. Zhang, and X. Chen. 2020. "On Two-tier Healthcare
        System Under Capacity Constraint." International Journal of Production
        Research 58 (12): 3744-3764. \\
        2. Wang, J., Z. Wang, Z. G. Zhang and F. Wang. 2021.
        ``Efficiency-quality trade-off in allocating resource to public
        healthcare systems.'' International Journal of Production Research, \\
        DOI:10.1080/00207543.2021.1992529}
    \end{itemize}

    These two papers are now discussed and included in the literature review
    section.

    \line(1, 0){0.92\textwidth}
    \begin{itemize}
        \item Reviewer 2: I gave a look into the new version and the comments
        made by the authors following the reviews they received.
        My criticism towards the paper as stated in the first round stays.
        It is basically the question of what are the standards of EJOR.
        If a paper which states a interesting model and gives details on
        numerical procedures for solving it but without any theorems and
        insights is good enough, then it should be accepted as the paper is
        doing a good job of what it promises.
        Otherwise, they should look for a more applied journal where what they
        do is sufficient.
    \end{itemize}

    We are grateful for the opportunity to respond to this as it seems that the 
    remaining concern is the fit of this work in EJOR and not the work itself.
    Firstly, this paper does provide theoretical results
    and insights.
    Section 3 provides detailed theoretical expressions of the queueing model's
    performance measures.
    Expressions of the waiting time, blocking time and proportion of
    individuals within target have been derived and are presented in the paper.
    Also, section 4.2 contains a list of applied scenarios where insights 
    are presented.
    A busy model is examined and insights on ways to increase the relative
    efficiency of the model are presented.

    We do understand the main point being raised by the reviewer in that this
    paper is not a purely theoretic one.
    For the benefits of the handling editor who we believe is left with the
    decision of whether or not the paper is in the scope of EJOR, here is a
    list of examples of papers published in EJOR that have a similar applied
    emphasis:
    \begin{itemize}
        \item[$\rhd$] \textbf{A queueing model for general group screening
        policies and dynamic item arrivals} published in 2010, Volume 207,
        Issue 2, by Dieter Claeys, Joris Walraevens, Koenraad Laevens and
        Herwig Bruneel \\
        https://doi.org/10.1016/j.ejor.2010.05.042
        \item[$\rhd$] \textbf{Selfish routing in public services} published in
        2013, Volume 230, Issue 1, by Vincent A.Knight and Paul R. Harper \\
        https://doi.org/10.1016/j.ejor.2013.04.003
        \item[$\rhd$] \textbf{The effect of ambulance relocations on the
        performance of ambulance service providers} published in 2016, Volume
        252, Issue 1, by T. C. van Barneveld, S. Bhulai and R.D.van der Mei \\
        https://doi.org/10.1016/j.ejor.2015.12.022
        \item[$\rhd$] \textbf{Robust and stochastic formulations for ambulance
        deployment and dispatch} published in 2019, Volume 279, Issue 2, by
        Dimitris Bertsimas and Yeesian Ng \\
        https://doi.org/10.1016/j.ejor.2019.05.011
        \item[$\rhd$] \textbf{A Markovian queueing model for ambulance offload
        delays} published in 2013, Volume 226, Issue 3, by Eman Almehdawe, Beth
        Jewkes and Qi-Ming He \\
        https://doi.org/10.1016/j.ejor.2012.11.030
        \item[$\rhd$] \textbf{Models and algorithms for an integrated vessel
        scheduling and tug assignment problem within a canal harbor} published
        in 2022, Volume 300, Issue 3, by Matteo Petris, Paola Pellegrini and
        Raffaele Pesenti \\
        https://doi.org/10.1016/j.ejor.2021.10.037
        \item[$\rhd$] \textbf{The application of operational research to
        European air traffic flow management - understanding the context}
        published in 2000, Volume 123, Issue 1, by Paula Leal de Matos and
        Richard Ormerod \\
        https://doi.org/10.1016/S0377-2217(99)00084-3
    \end{itemize}
    
    Finally, we note that the aims and scope of EJOR do not emphasise that a paper
    should present a new theorem in order to be published.
    Here's the aim and scope of EJOR as listed in their website: \\[0.5cm]
    \textit{
        The European Journal of Operational Research (EJOR) publishes high
        quality, original papers that contribute to the methodology of operational
        research (OR) and to the practice of decision making. EJOR contains the
        following types of papers:
        \begin{itemize}
            \item[$\square$] Invited Reviews, explaining to the general OR audience the developments in an OR topic over the recent years
            \item[$\square$] Innovative Applications of OR, describing novel ways to solve real problems
            \item[$\square$] Theory and Methodology Papers, presenting original research results contributing to the methodology of OR and to its theoretical foundations,
            \item[$\square$] Short Communications, if they correct important errors found in papers previously published in EJOR
        \end{itemize}
    }
    
    \line(1, 0){0.92\textwidth}
    \begin{itemize}
        \item Reviewer 3: \textit{The authors handled my remarks well.}
    \end{itemize}
    Thank you.

\end{document}